\documentclass[11pt]{report}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[explicit]{titlesec}
\usepackage{color, varwidth}
\usepackage[margin=0.75in]{geometry}
\usepackage{xhfill}
\usepackage{soul}
\graphicspath{{./images/}}

%----------------------------------------------------------------------------------------
%	SECTION HEADER STYLES
%----------------------------------------------------------------------------------------
\setlength{\headheight}{15pt}

\definecolor{darkblue}{RGB}{0,101,135}
\definecolor{ourblue}{RGB}{0,138,184}

\newcommand{\hsp}{\hspace{20pt}}
\titleformat{\chapter}[hang]{\huge\bfseries}{\thechapter\hsp\textcolor{ourblue}{|}\hsp}{0pt}{#1\Huge\bfseries}

\newcommand\Centered{%
\titleformat{\section}[hang]
  {\normalfont\large\filcenter}{}{0em}
  {\xrfill[0.3ex]{1.0pt}[ourblue]~\begin{varwidth}{.75\linewidth}\centering{\color{darkblue}##1}\end{varwidth}~\xrfill[0.3ex]{1.0pt}[ourblue]}
}

\newcommand\textline[4][t]{%
  \par\smallskip\noindent\parbox[#1]{.333\textwidth}{\raggedright#2}%
  \parbox[c]{.333\textwidth}{\centering#3}%
  \parbox[c]{.333\textwidth}{\raggedleft#4}\par\smallskip%
  \vspace{.5\baselineskip}
}

\titlespacing{\chapter}{12pt plus 4pt minus 2pt}{\parskip}{7pt}


\renewcommand\sectionmark[1]{\markboth{#1}{}}

%----------------------------------------------------------------------------------------

\begin{document}

\input{./title.tex}

\pagebreak

\chapter{Sprint Overview}
This sprint, being our first sprint aims to set up the basic framework we need to develop Synchronizo. A lot of this will involve having our more experienced team members teach and guide the others in the basics of web development and getting a good development work-flow set up. This will also include setting up the architecture to host the Synchronizo website, making a very basic front-end and setting up the boilerplate node.js code for the web app. It will also include our first attempt to allow for music uploads on the website.

\begin{description}
\item[Scrum Master] Abhijeet Chakrabarti

\item[Meeting Plan] Meeting on Fridays and Saturdays in Hillenbrand

\item[Risks And Challenges] Some of the members of our team are not yet familiar with web development practices or skilled in the languages required to create our web-app. For our team, a large part of Sprint 1 will be attempting to bring all of the members of our team up to speed with the technical skills required to complete this project.
\end{description}

\chapter{Current Sprint Details}

\Centered{
    \section{User Story \#2}
}

As a user, I want to be able to upload my own music.

\vspace{3mm}

\def\arraystretch{1.6}%  1 is the default, change whatever you need 
\begin{tabular}{c|c|c|c|c}
     \# & Description & Time & Team & Owner \\
     \hline
     1  & Create a basic upload page       & 3 hrs & Front-End & Eric \\
     2  & Make back-end handle file uploads & 3 hrs & Back-End  & Eric \\
     3  & Configure uploading to handle different file types & 5 hrs & Back-End & Eric \\
     4  & Make back-end and front-end report upload progress & 4 hrs & Back-End and Front-End & Ammar \\
     5  & Transcode file uploads to a unified format & 2 hrs & Back-End & Eric
\end{tabular}

\vspace{4mm}

\subsection*{Acceptance Criteria}
\begin{itemize}
    \item \textit{Given} uploads have been implemented, \textit{when} I go to the Synchronizo webapp, \textit{then} I should see some sort of interface
    that allows me to upload my own files.
    
    \item \textit{Given} that there is an interface that allows me to upload files, \textit{when} it is used to upload a file, \textit{then} there should be some sort of indicator of the progress of the upload.
    
    \item \textit{Given} that a file is upload successfully, \textit{when} the upload is finished, \textit{then} it should be converted into a single format such as mp3 so that it may be used universally.
\end{itemize}


\Centered{
    \section{User Story \#18}
}

As a user, I want to be able to see information about the album for playing tracks.

\vspace{3mm}

\begin{tabular}{c|c|c|c|c}
     \# & Description & Time & Team & Owner \\
     \hline
     1  & Create an optional text section for album info & 2 hrs & Front-End & Abhijeet\\
     2  & Make back-end communicate with last.fm's API & 3 hrs & Back-End  & Ammar \\
     3  & Obtain album info from API and display it & 3 hrs & Back-End and Front-End & Ammar \\
\end{tabular}

\vspace{4mm}

\subsection*{Acceptance Criteria}
\begin{itemize}
    \item \textit{Given} an uploaded music file, \textit{when} it is done uploading, \textit{then} information about its album should be retrieved from the last.fm API.
    
    \item \textit{Given} an uploaded music file, \textit{when} it is displayed on the webapp, \textit{then} information about the album of the song should be displayed.
    
    \item \textit{Given} an uploaded music file, \textit{when} information about it cannot be retrieved, \textit{then} an indicator of a failure to retrieve the metadata should be shown.
\end{itemize}

\pagebreak

\Centered{
    \section{User Story \#19}
}

As a user, I want to be able to see information about the artist for playing tracks.

\vspace{3mm}

\begin{tabular}{c|c|c|c|c}
     \# & Description & Time & Team & Owner \\
     \hline
     1  & Create an optional text section for artist info & 2 hrs & Front-End & Abhijeet \\
     2  & Obtain artist info from last.fm API and display it & 2 hrs & Front-end and Back-End  & Brian \\
    
\end{tabular}

\vspace{4mm}

\subsection*{Acceptance Criteria}
\begin{itemize}
    \item \textit{Given} an uploaded music file, \textit{when} it is done uploading, \textit{then} information about its artist should be retrieved from the last.fm API.
    
    \item \textit{Given} an uploaded music file, \textit{when} it is displayed on the webapp, \textit{then} artist information should be visible.
\end{itemize}


\Centered{
    \section{User Story \#3}
}

As a user, I want to be able to create an account.

\vspace{3mm}

\begin{tabular}{c|c|c|c|c}
     \# & Description & Time & Team & Owner \\
     \hline
     1  & Create a basic sign up page & 3 hrs & Front-End & Abhijeet \\
     2  & Set up database to handle creation of users & 6 hrs & Back-End  & Ammar \\
     3  & Create a record for the user in the database when they register & 4 hrs & Back-End & Ammar
    
\end{tabular}

\vspace{4mm}

\subsection*{Acceptance Criteria}
\begin{itemize}
    \item \textit{Given} a user goes to the webapp, \textit{when} they hit the sign-up button, \textit{then} they should be brought to a page where they can enter their registration details and sign up for the site.
    
    \item \textit{Given} a user signs up, \textit{when} they finish the sign up process, \textit{then} a record representing them should be added to the database.
\end{itemize}


\Centered{
    \section{User Story \#4}
}

As a user, I want to be able to log in to my account.

\vspace{3mm}

\begin{tabular}{c|c|c|c|c}
     \# & Description & Time & Team & Owner \\
     \hline
     1  & Create a basic login page & 5 hrs & Front-End & Brian \\
     2  & Handle authentication and session creation on the back-end & 3 hrs & Back-End & Brian\\
     3  & Make session handling code to handle timeouts & 2 hrs & Back-End & Brian
    
\end{tabular}

\vspace{4mm}

\subsection*{Acceptance Criteria}
\begin{itemize}
    \item \textit{Given} a signed up user, \textit{when} they go to login, \textit{then} they should be able to enter their
    login details and be able to login.
    
    \item \textit{Given} a logged in user, \textit{when} they go to the webapp, \textit{then} there should be some indication that they are logged in.
    
    \item \textit{Given} a logged in user, \textit{when} they have been inactive for a certain period of time, \textit{then} their session should expire and they should be logged out automatically.
    
\end{itemize}


\chapter{Remaining Backlog}
    
    \begin{enumerate}

    \item As a user, I want to be able to listen to music simultaneously with other people.
    
    \item As a user, I want to to be able to upload my own music.
        
    \item As a user, I want to be able to create an account.
    
    \item As a user, I want to be able to log in to my account.

    \item As a user, I want to be able to have people follow my account.

    \item As a user, I want to be able to follow other users.
    
    \item As a user, I want to be able to un-follow other users.
    
    \item As a user, I want to be able to party chat with other users in the same listening party.
    
    \item As a user, I want to be able to direct message other users.
    
    \item As a user, I want to be able to invite other users to join my listening party.
    
    \item As a user, I want to be able to permanently leave certain listening parties.
    
    \item As a user, I want my followers to be able to see the recent music I have listened to.
    
    \item As a user, I want the ability to block other users. 
    
    \item As a user, I want the ability to report other users for misconduct.
    
    \item As a user, I want to have a profile (picture, bio, favorite music, etc.)
    
    \item As a user, I want to be able to set privacy settings for my account.
    
    \item As a user, I want to be able to create multiple listening parties.
    
    \item As a user, I want to be able to see information about the album for playing tracks.
    
    \item As a user, I want to be able to see information about the artist for playing tracks.

    \item As a user, I want to be able to control the playback of the music for everyone.
    
    \item As a user, I want to be able to view listener metrics and statistics.
    
    \item As an admin, I want to be able to control user accounts.
    
    \item As an admin, I want to be able to monitor usage of the service.
    
    \item As an advertiser, I want to be able to see data on people's taste in music so I can target ads to them.

\end{enumerate}

\end{document}